SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
changes in the exploitation model

\begin{IEEEkeywords}
Security and Protection, Application Security, Code injection Attacks,
Testing, Cross-Site Scripting.
\end{IEEEkeywords}

@@

A recent class of code injection attacks involve dynamic languages
like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
A simple example of a dynamic language-driven attack is an input string
that is fed into an {\tt eval()} function call, e.g., in {\sc php}:

@@

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick an end user to click on it via social
engineering (i.e., phishing, through transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code in the application (through
transition {\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
in a web application that accepts and redisplays user input
without appropriate validation. An attacker could upload data
containing a specially crafted script (for example, in a blog comment)
to steal the cookies of the visiting users or embed malicious {\sc
  sql} code to retrieve all the password entries from a database. Note that
an {\sc xss} attack can start from both routes.

Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from now on. In an {\sc sql} injection
attack the injected code becomes part of a query that
finally reaches the database where it is executed.

@@

Application attack defense mechanisms
must demonstrate the presence of an attack. This, however, does not
make an application attack defense mechanism immediately useful. A
detection mechanism must be reliable. The accuracy of a detection
mechanism is gauged with the following
metrics~\cite{TDR2013,GFDLS06,A00}:
\begin{itemize}
\item {\bf Sensitivity}, the probability that an attack will be
  caught.
\item {\bf Specificity}, the probability that a normal interaction
  will test negative.
\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
  nothing is reported no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}

@@

Defenses based on training include some mechanisms that can be easily
circumvented. For example, {\sc didafit} and {\it libAnomaly} do not
tag transactions with their corresponding call sites. This can lead
easily to false negatives. For instance, the application
mentioned in Section~\ref{sec:attacks}, which will send the password
for a forgetful user via email by executing the following query:

@@

\noindent
Even if the application's administrators have chosen to use
either {\sc didafit} or {\it libAnomaly}, an attacker could bypass
them and obtain the administrator's password via email,
by entering on the form the standard string:
{\tt nosuchuser' OR id = 'admin}. The infected query matches the
signature of the second one above and is therefore accepted.
The problem lies with the call location of the query, not the query alone.

>>>>

\begin{IEEEkeywords}
Security and Protection, Web Application Security, Code injection Attacks,
Testing, Cross-Site Scripting.
\end{IEEEkeywords}

@@

A recent class of code injection attacks involve dynamic languages
like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
A simple example of a {\sc php} injection attack is an input string
that is fed into an {\tt eval()} function call, e.g., in {\sc php}:

@@

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick an end user to click on it via social
engineering (i.e., phishing, through transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code in the application (through
transition {\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
in a web application that accepts and redisplays user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users or embed malicious
{\sc sql} code to retrieve all the password entries from a database.
Recall the examples we provided in Section~\ref{sec:attacks}.
Note that an {\sc xss} attack can start from both routes.

Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from now on. In an {\sc sql} injection
attack the injected code becomes part of a query that
finally reaches the database where it is executed.
In the case of a {\sc csrf} attack the functionality dictated by
the malicious response is performed.

@@

Web application attack defense mechanisms
must demonstrate the presence of an attack. This, however, does not
make an application attack defense mechanism immediately useful. A
detection mechanism must be reliable. The accuracy of a detection
mechanism is gauged with the following
metrics~\cite{TDR2013,GFDLS06,A00}:
\begin{itemize}
\item {\bf Sensitivity}, the probability that an attack will be
  caught.
\item {\bf Specificity}, the probability that a normal interaction
  will test negative.
\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
  nothing is reported no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}

@@

Defenses based on training include some mechanisms that can be easily
circumvented. For example, {\sc didafit} and {\it libAnomaly} do not
tag transactions with their corresponding call sites. This can lead
easily to false negatives. For instance, recall the application
mentioned in Section~\ref{sec:attacks}, which will send the password
for a forgetful user via email by executing the following query:

@@

\noindent
Even if the application's administrators have chosen to use
either {\sc didafit} or {\it libAnomaly} as protection,
an attacker could bypass them and obtain the
administrator's password via email,
by entering on the form the standard string:
{\tt nosuchuser' OR id = 'admin}. The infected query matches the
signature of the second one above and is therefore accepted.
The problem lies with the call location of the query, not the query alone.
